A biometric analysis of infant mortality and temperature, northern Sweden 1895-1950

### 2022-01-23 paper.Rmd
truncate cold in postneonatal

```{r postanal, results='asis'}
infdat$parity <- cut(infdat$parity, c(-2, 1.5, 4.5, 19), labels = c("1", "2-4", "5+"))
infdat$period <- cut(infdat$birthdate, c(1895, 1914, 1935, 1951), dig.lab = 5)
levels(infdat$subreg) <- c("ume", "ske")
infdat$season <- cut(infdat$week, c(-1, 9.5, 22.5, 35.5, 48.5, 52.5), labels = c("winter", "spring", "summer", "fall", "winter"))
infdat$season <- as.factor(infdat$season)
pneo <- age.window(infdat, c(28 / 365, 1))
##
pneo$enter <- g(pneo$enter * 365)
pneo$exit <- g(pneo$exit * 365)
##
pneo$emintemp <- round(pneo$emintemp)
##
tpneo <- toTpch(Surv(enter, exit, event) ~ sex + socBranch + socStatus + illeg + parity + 
                    period + cold
                + emintemp + season + subreg, 
                data = pneo, cuts = g(c(28, 365)))
##fit2 <- phreg(Surv(enter - g(28), exit - g(28), event) ~ sex + socBranch + socStatus + cold + emintemp, 
  ##           data = pneo, shape = 1)
##fit.pch <- pchreg(Surv(enter, exit, event) ~ sex + socBranch + socStatus + cold + emintemp, 
  ##           data = pneo, cuts = g(c(28, 365)))
fit.tpch <- tpchreg(oe(event, exposure) ~ sex + socBranch + socStatus + illeg + parity +
                        period + cold + emintemp + season + subreg, 
                    data = tpneo, time = age)
dr <- drop1(fit.tpch, test = "Chisq")
ltx(fit.tpch, dr = dr, caption = "Postneonatal mortality.", label = "tab:postanal")
```

@@

>>>>

```{r postanalske, results='asis'}
infdat$parity <- cut(infdat$parity, c(-2, 1.5, 4.5, 19), labels = c("1", "2-4", "5+"))
infdat$period <- cut(infdat$birthdate, c(1895, 1914, 1935, 1951), dig.lab = 5)
levels(infdat$subreg) <- c("ume", "ske")
infdat$season <- cut(infdat$week, c(-1, 9.5, 22.5, 35.5, 48.5, 52.5), labels = c("winter", "spring", "summer", "fall", "winter"))
infdat$season <- as.factor(infdat$season)
pneo <- age.window(infdat, c(28 / 365, 1))
##
pneo$enter <- g(pneo$enter * 365)
pneo$exit <- g(pneo$exit * 365)
##
pneo$emintemp <- round(pneo$emintemp)
##
tpneo <- toTpch(Surv(enter, exit, event) ~ period + sex + socBranch + socStatus + illeg + parity + 
                    cold 
                + emintemp + season + subreg, 
                data = pneo, cuts = g(c(28, 365)))
##fit2 <- phreg(Surv(enter - g(28), exit - g(28), event) ~ sex + socBranch + socStatus + cold + emintemp, 
  ##           data = pneo, shape = 1)
##fit.pch <- pchreg(Surv(enter, exit, event) ~ sex + socBranch + socStatus + cold + emintemp, 
  ##           data = pneo, cuts = g(c(28, 365)))
tpneo$icold <- with(tpneo, cold * (cold < 0))
fit.tpch <- tpchreg(oe(event, exposure) ~ icold + emintemp + season +  period + sex + socBranch + socStatus  + parity, 
                    data = tpneo[tpneo$subreg == "ske", ], time = age)
dr <- drop1(fit.tpch, test = "Chisq")
ltx(fit.tpch, dr = dr, caption = "Postneonatal mortality, Skellefteå.", label = "tab:postanalske")
```

@@

```{r postanalume, results = 'asis'}
fit.tpch <- tpchreg(oe(event, exposure) ~ icold + period + sex + socBranch + socStatus + period  + parity +
                        season, 
                    data = tpneo[tpneo$subreg == "ume", ], time = age)
dr <- drop1(fit.tpch, test = "Chisq")
ltx(fit.tpch, dr = dr, caption = "Postneonatal mortality, Umeå.", label = "tab:postanalume")
```
